---
title: "Visualizing Game Sales"
author: "Jason Liu"
date: "Oct 29,2016"
output: 
     html_document:
            toc: true
            highlight: zenburn
            fig_height: 7
            fig_width: 10
            theme: journal
---
# Introduction

The motivation of this Kernel is to show and practice exploratory analysis of data set. Thanks for the contribution from **GregorySmith**. In order to better visualize the data, I choose to use package **plotly** to creat interactive plots.

# Read Data

```{r,message=FALSE,warning=FALSE}
library(sqldf)
library(fmsb)
library(plotly)
df<-read.csv('vgsales.csv')
df[df=="N/A"]<-NA
df<-df[complete.cases(df),]
df$Year<-as.numeric(as.character(df$Year))
df<-df[df$Year<=2016,]
summary(df)
```

# Explore Sales by Year and Platform {.tabset}

```{r,message=FALSE,warning=FALSE}
ByYear<-sqldf("SELECT Platform, Year, sum(NA_Sales) as AME, sum(EU_Sales) as EU,sum(JP_Sales) as JP, sum(Other_Sales) as Other, sum(Global_Sales) as Global from df group by Platform, Year order by Year,Platform")

```

## All Platforms

```{r results='asis',message=FALSE,warning=FALSE}
All<- sqldf("SELECT Year, sum(NA_Sales) as AME, sum(EU_Sales) as EU,sum(JP_Sales) as JP, sum(Other_Sales) as Other, sum(Global_Sales) as Global from df group by Year order by Year")

plot_ly(y=All$EU,x=All$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=All$AME,x=All$Year,name='American Sale',type='lines')%>%
  add_trace(y=All$Global,x=All$Year,name='Global Sale',type='lines')%>%
  add_trace(y=All$JP,x=All$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=All$Other,x=All$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in All Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))


```

## DS

```{r results='asis',message=FALSE,warning=FALSE}
DS<-ByYear[ByYear$Platform=='DS',]
plot_ly(y=DS$EU,x=DS$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=DS$AME,x=DS$Year,name='American Sale',type='lines')%>%
  add_trace(y=DS$Global,x=DS$Year,name='Global Sale',type='lines')%>%
  add_trace(y=DS$JP,x=DS$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=DS$Other,x=DS$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in DS Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))
```

## PS


```{r results='asis',message=FALSE,warning=FALSE}
PS<-ByYear[ByYear$Platform=='PS',]
plot_ly(y=PS$EU,x=PS$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=PS$AME,x=PS$Year,name='American Sale',type='lines')%>%
  add_trace(y=PS$Global,x=PS$Year,name='Global Sale',type='lines')%>%
  add_trace(y=PS$JP,x=PS$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=PS$Other,x=PS$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in PS Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))
```


## PS2

```{r results='asis',message=FALSE,warning=FALSE}
PS2<-ByYear[ByYear$Platform=='PS2',]
plot_ly(y=PS2$EU,x=PS2$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=PS2$AME,x=PS2$Year,name='American Sale',type='lines')%>%
  add_trace(y=PS2$Global,x=PS2$Year,name='Global Sale',type='lines')%>%
  add_trace(y=PS2$JP,x=PS2$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=PS2$Other,x=PS2$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in PS2 Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))
```

## PS3


```{r results='asis',message=FALSE,warning=FALSE}
PS3<-ByYear[ByYear$Platform=='PS3',]
plot_ly(y=PS3$EU,x=PS3$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=PS3$AME,x=PS3$Year,name='American Sale',type='lines')%>%
  add_trace(y=PS3$Global,x=PS3$Year,name='Global Sale',type='lines')%>%
  add_trace(y=PS3$JP,x=PS3$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=PS3$Other,x=PS3$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in PS3 Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))
```

## Wii

```{r results='asis',message=FALSE,warning=FALSE}
Wii<-ByYear[ByYear$Platform=='Wii',]
plot_ly(y=Wii$EU,x=Wii$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=Wii$AME,x=Wii$Year,name='American Sale',type='lines')%>%
  add_trace(y=Wii$Global,x=Wii$Year,name='Global Sale',type='lines')%>%
  add_trace(y=Wii$JP,x=Wii$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=Wii$Other,x=Wii$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in Wii Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))
```

## X360

```{r results='asis',message=FALSE,warning=FALSE}
X360<-ByYear[ByYear$Platform=='X360',]
plot_ly(y=X360$EU,x=X360$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=X360$AME,x=X360$Year,name='American Sale',type='lines')%>%
  add_trace(y=X360$Global,x=X360$Year,name='Global Sale',type='lines')%>%
  add_trace(y=X360$JP,x=X360$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=X360$Other,x=X360$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in X360 Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))
```

## PSP

```{r results='asis',message=FALSE,warning=FALSE}
PSP<-ByYear[ByYear$Platform=='PSP',]
plot_ly(y=PSP$EU,x=PSP$Year,type='lines',name='Europe Sale')%>%
  add_trace(y=PSP$AME,x=PSP$Year,name='American Sale',type='lines')%>%
  add_trace(y=PSP$Global,x=PSP$Year,name='Global Sale',type='lines')%>%
  add_trace(y=PSP$JP,x=PSP$Year,name='Japen Sales',type='lines')%>%
  add_trace(y=PSP$Other,x=PSP$Year,name='Other Regions',type='lines')%>%
  layout(title = "Sales in PSP Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))
```

# Explore Sales by Region and Platform {.tabset}

## Global

```{r results='asis',message=FALSE,warning=FALSE}
Main_platform<-c('DS','PS','PS2','PS3','Wii','X360','PSP')
ByRegion<-sqldf("SELECT Platform,sum(NA_Sales) as AME, sum(EU_Sales) as EU,sum(JP_Sales) as JP, sum(Other_Sales) as Other, sum(Global_Sales) as Global from df group by Platform")
JP<-sum(ByRegion[!ByRegion$Platform %in% Main_platform,]$JP)
AME<-sum(ByRegion[!ByRegion$Platform %in% Main_platform,]$AME)
EU<-sum(ByRegion[!ByRegion$Platform %in% Main_platform,]$EU)
Global<-sum(ByRegion[!ByRegion$Platform %in% Main_platform,]$Global)
Other<-sum(ByRegion[!ByRegion$Platform %in% Main_platform,]$Other)
New_row<-data.frame(Platform='Others',AME=AME,EU=EU,JP=JP,Other=Other,Global=Global)
ByRegion<-ByRegion[ByRegion$Platform%in%Main_platform,]
ByRegion<-rbind(ByRegion,New_row)
Global<-ByRegion[,c('Platform','Global')]
plot_ly(labels=Global$Platform,values=Global$Global,type='pie') %>%
  layout(title = 'Global Sales by Platform',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

## North America

```{r results='asis',message=FALSE,warning=FALSE}
AME<-ByRegion[,c('Platform','AME')]
plot_ly(labels=AME$Platform,values=AME$AME,type='pie') %>%
  layout(title = 'North America Sales by Platform',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

## Europe

```{r results='asis',message=FALSE,warning=FALSE}
EU<-ByRegion[,c('Platform','EU')]
plot_ly(labels=EU$Platform,values=EU$EU,type='pie') %>%
  layout(title = ' Europe Sales by Platform',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

## Japan


```{r results='asis',message=FALSE,warning=FALSE}
JP<-ByRegion[,c('Platform','JP')]
plot_ly(labels=JP$Platform,values=JP$JP,type='pie') %>%
  layout(title = 'Japan Sales by Platform',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

## Other Regions

```{r results='asis',message=FALSE,warning=FALSE}
Other<-ByRegion[,c('Platform','Other')]
plot_ly(labels=Other$Platform,values=Other$Other,type='pie') %>%
  layout(title = ' Sales of other regions by Platform',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

# Explore Sales By Genere

## By Region and Genre{.tabset}

### Global

```{r results='asis',message=FALSE,warning=FALSE}
Region_Genre<- sqldf("SELECT Genre,sum(NA_Sales) as AME, sum(EU_Sales) as EU,sum(JP_Sales) as JP, sum(Other_Sales) as Other, sum(Global_Sales) as Global from df group by Genre")
Global<-Region_Genre[,c('Genre','Global')]
plot_ly(y=Global$Global,x=Global$Genre,type='bar')%>%
  layout(title = "Global Sales by Genre",
         scene = list(
           xaxis = list(title = "Genre"), 
           yaxis = list(title = "Sales")))
  
```

### North America

```{r results='asis',message=FALSE,warning=FALSE}
AME<-Region_Genre[,c('Genre','AME')]
plot_ly(y=AME$AME,x=AME$Genre,type='bar')%>%
  layout(title = "AME Sales by Genre",
         scene = list(
           xaxis = list(title = "Genre"), 
           yaxis = list(title = "Sales")))

```

### Europe

```{r results='asis',message=FALSE,warning=FALSE}
EU<-Region_Genre[,c('Genre','EU')]
plot_ly(y=EU$EU,x=EU$Genre,type='bar')%>%
  layout(title = "EU Sales by Genre",
         scene = list(
           xaxis = list(title = "Genre"), 
           yaxis = list(title = "Sales")))


```

### Japan

```{r results='asis',message=FALSE,warning=FALSE}
JP<-Region_Genre[,c('Genre','JP')]
plot_ly(y=JP$JP,x=JP$Genre,type='bar')%>%
  layout(title = "JP Sales by Genre",
         scene = list(
           xaxis = list(title = "Genre"), 
           yaxis = list(title = "Sales")))


```

### Other Regions

```{r results='asis',message=FALSE,warning=FALSE}
Other<-Region_Genre[,c('Genre','Other')]
plot_ly(y=Other$Other,x=Other$Genre,type='bar')%>%
  layout(title = "Other Sales by Genre",
         scene = list(
           xaxis = list(title = "Genre"), 
           yaxis = list(title = "Sales")))
```

## By Platform and Genre{.tabset}

### DS

```{r results='asis',message=FALSE,warning=FALSE}
Platform_Genere<- sqldf('SELECT Genre, Platform, sum(Global_Sales) as Sales from df group by Genre,Platform')
Platform_Genere<-Platform_Genere[Platform_Genere$Platform%in%Main_platform,]
DS<-Platform_Genere[Platform_Genere$Platform=='DS',]
plot_ly(labels = DS$Genre, values = DS$Sales,type='pie',hole=0.6) %>%
  layout(title = "Genre of Games on DS",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### PS

```{r results='asis',message=FALSE,warning=FALSE}
PS<-Platform_Genere[Platform_Genere$Platform=='PS',]
plot_ly(labels = PS$Genre, values = PS$Sales,type='pie',hole=0.6) %>%
  layout(title = "Genre of Games on PS",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

### PS2

```{r results='asis',message=FALSE,warning=FALSE}
PS2<-Platform_Genere[Platform_Genere$Platform=='PS2',]
plot_ly(labels = PS2$Genre, values = PS2$Sales,type='pie',hole=0.6) %>%
  layout(title = "Genre of Games on PS2",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

### PS3

```{r results='asis',message=FALSE,warning=FALSE}
PS3<-Platform_Genere[Platform_Genere$Platform=='PS3',]
plot_ly(labels = PS3$Genre, values = PS3$Sales,type='pie',hole=0.6) %>%
  layout(title = "Genre of Games on PS3",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### Wii

```{r results='asis',message=FALSE,warning=FALSE}
Wii<-Platform_Genere[Platform_Genere$Platform=='Wii',]
plot_ly(labels = Wii$Genre, values = Wii$Sales,type='pie',hole=0.6) %>%
  layout(title = "Genre of Games on Wii",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### X360

```{r results='asis',message=FALSE,warning=FALSE}
X360<-Platform_Genere[Platform_Genere$Platform=='X360',]
plot_ly(labels = X360$Genre, values = X360$Sales,type='pie',hole=0.6) %>%
  layout(title = "Genre of Games on X360",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### PSP

```{r results='asis',message=FALSE,warning=FALSE}
PSP<-Platform_Genere[Platform_Genere$Platform=='PSP',]
plot_ly(labels = PSP$Genre, values = PSP$Sales,type='pie',hole=0.6) %>%
  layout(title = "Genre of Games on PSP",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

# Explore the top 5 Publishers

```{r,message=FALSE, warning=FALSE}
Publisher<- sqldf('SELECT Publisher, sum(Global_Sales) as Sales from df group by Publisher order by Sales desc')[c(1:5),]
print(Publisher[,1])
```

## Sales across Regions{.tabset}

### Nintendo

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[1,1],]
frame<-data.frame(Region=c('North America','Europe','Japan','Other Regions'),Sales=c(sum(tmp$NA_Sales),sum(tmp$EU_Sales),sum(tmp$JP_Sales),sum(tmp$Other_Sales)))

plot_ly(labels =frame$Region, values =frame$Sales,type='pie',hole=0.4)%>%
  layout(title = "Sales Proportion by Regions",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

### Electronic Arts

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[2,1],]
frame<-data.frame(Region=c('North America','Europe','Japan','Other Regions'),Sales=c(sum(tmp$NA_Sales),sum(tmp$EU_Sales),sum(tmp$JP_Sales),sum(tmp$Other_Sales)))

plot_ly(labels =frame$Region, values =frame$Sales,type='pie',hole=0.4)%>%
  layout(title = "Sales Proportion by Regions",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

### Activision

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[3,1],]
frame<-data.frame(Region=c('North America','Europe','Japan','Other Regions'),Sales=c(sum(tmp$NA_Sales),sum(tmp$EU_Sales),sum(tmp$JP_Sales),sum(tmp$Other_Sales)))

plot_ly(labels =frame$Region, values =frame$Sales,type='pie',hole=0.4)%>%
  layout(title = "Sales Proportion by Regions",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

### Sony

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[4,1],]
frame<-data.frame(Region=c('North America','Europe','Japan','Other Regions'),Sales=c(sum(tmp$NA_Sales),sum(tmp$EU_Sales),sum(tmp$JP_Sales),sum(tmp$Other_Sales)))

plot_ly(labels =frame$Region, values =frame$Sales,type='pie',hole=0.4)%>%
  layout(title = "Sales Proportion by Regions",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

### Ubisoft

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[5,1],]
frame<-data.frame(Region=c('North America','Europe','Japan','Other Regions'),Sales=c(sum(tmp$NA_Sales),sum(tmp$EU_Sales),sum(tmp$JP_Sales),sum(tmp$Other_Sales)))

plot_ly(labels =frame$Region, values =frame$Sales,type='pie',hole=0.4)%>%
  layout(title = "Sales Proportion by Regions",  showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

## Sales across Platforms{.tabset}

### Nintendo

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[1,1],]
frame<-sqldf('SELECT Platform, sum(Global_Sales) as Sales from tmp group by Platform')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )
```

### Electronic Arts

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[2,1],]
frame<-sqldf('SELECT Platform, sum(Global_Sales) as Sales from tmp group by Platform')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )
```

### Activision

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[3,1],]
frame<-sqldf('SELECT Platform, sum(Global_Sales) as Sales from tmp group by Platform')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )

```

### Sony

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[4,1],]
frame<-sqldf('SELECT Platform, sum(Global_Sales) as Sales from tmp group by Platform')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )

```

### Ubisoft

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[5,1],]
frame<-sqldf('SELECT Platform, sum(Global_Sales) as Sales from tmp group by Platform')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )
```

## Sales across Genres{.tabset}

### Nintendo

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[1,1],]
frame<-sqldf('SELECT Genre, sum(Global_Sales) as Sales from tmp group by Genre')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )
```

### Electronic Arts

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[2,1],]
frame<-sqldf('SELECT Genre, sum(Global_Sales) as Sales from tmp group by Genre')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )
```

### Activision

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[3,1],]
frame<-sqldf('SELECT Genre, sum(Global_Sales) as Sales from tmp group by Genre')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )

```

### Sony

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[4,1],]
frame<-sqldf('SELECT Genre, sum(Global_Sales) as Sales from tmp group by Genre')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )

```

### Ubisoft

```{r results='asis',message=FALSE,warning=FALSE}
tmp<-df[df$Publisher==Publisher[5,1],]
frame<-sqldf('SELECT Genre, sum(Global_Sales) as Sales from tmp group by Genre')
frame_t<- t(frame[,2:ncol(frame)])
colnames(frame_t)<-frame[,1]
frame_t<-as.data.frame(frame_t)
data=rbind(rep(max(frame$Sales),ncol(frame_t)) , rep(min(frame$Sales),ncol(frame_t)) , frame_t)
radarchart(data, axistype=1 , 
pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
vlcex=0.8 )
```


# Concluding Remark

This Kernel presents some basic exploratory analysis of the data set. Further suggestions and instructions are **extremely welcomed**.
