---
title: "911 Emergency"
author: "Jason Liu"
date: "Oct 24,2016"
output: html_document
---
## Analyzing and Visualizing 911 Calls by GoogleVis

This kernel serves the purpose of presenting quick data analytic with Google Visulization. The analysis will mainly focus on two aspects: Geographical information and time stamp of the calls.

### Fire up

```{r,message=FALSE, warning=FALSE}
library(googleVis)
library(sqldf)
library(ggmap)
library(ggplot2)
Sys.setenv(LANG = "en")
Sys.setlocale("LC_TIME", "C")
data<-read.csv('911.csv')
df<-data[,c('lat','lng','title','timeStamp')]
summary(df)
```

### Data Pre-processing

Before analysis, we first perform data preprocessing step for a more neat dataset. First, we split the title of the event.

```{r, echo=FALSE}
df<-data.frame(df,Event_type=NA,Event_detail=NA)
df$Event_type<-sapply(df$title,function(x) strsplit(as.character(x),':')[[1]][1])
df$Event_detail<-sapply(df$title,function(x) strsplit(as.character(x),':')[[1]][2])
```


Next, we will deal with timeStamp of the 911 calls.

```{r,message=FALSE,warning=FALSE}
df<-data.frame(df,Date=NA,Time=NA,Hour=NA,Days=NA,Period=NA)
df$Date<-sapply(df$timeStamp,function(x) strsplit(as.character(x),' ')[[1]][1])
df$Time <- sapply(df$timeStamp,function(x) strsplit(as.character(x),' ')[[1]][2] )
df$Hour<-sapply(df$Time,function(x) as.numeric(strsplit(as.character(x),':')[[1]][1]))
df$Period<-sapply(df$Hour,function(x){
  nu<-x
  if(nu>6&&nu<=12){
   'Morining'
  }else if(nu>12&&nu<=18){
    'Afternoon'
  }else if(nu>18&&nu<=24){
     'Evening'
  }else{
    'Midnight'
    }
}
)
c<-as.Date(df$Date)
df$Date<-c
cc<-weekdays(c)
df$Days<-cc
```

Then, the data are all in the form we want. I will divide the analytics in terms of the type of events so the whole procedure will be transparent and efficient.

### Build functions for analytic

In order to make the analysis and plot more direct and efficient, I choose to wrap up the analyzes into differnt functions so that the subsquent procedures will be boosted.

**A: Where do these calls happen? **

```{r,message=FALSE,warning=FALSE}
map_d<-qmap('Philadelphia', zoom = 9, maptype = 'hybrid')
Map<-function(item){
  color<-list('EMS'='Yellow','Fire'='red','Traffic'='blue')
  if(item=='All'){
    tmp<-df
  }else{
    tmp<-df[df$Event_type==item,]
  }
  if(item=='All'){
  plt<-map_d + geom_point(data = tmp, aes(x = lng, y = lat,color=Event_type), alpha=0.5)
  }
  else{
  plt<-map_d + geom_point(data = tmp, aes(x = lng, y = lat), color=color[item], alpha=0.5) 
  }
  return(plot(plt))
}

```

**B: Calls among days of a week**

```{r results='asis',message=FALSE,warning=FALSE}
days<-function(item){
if(item=='All'){
    tmp<-df
  }else{
    tmp<-df[df$Event_type==item,]
  }
tmp<-sqldf('SELECT Days,count(Days) as freq from tmp group by Days')
dayp<-gvisColumnChart(tmp,options = list(width=800,height=600))
return(dayp)
}
```

**C: Calls among periods**

```{r results='asis',message=FALSE,warning=FALSE}
period<-function(item){
if(item=='All'){
    tmp<-df
  }else{
    tmp<-df[df$Event_type==item,]
  }
tmp<-sqldf('SELECT Period,count(Period) as freq from tmp group by Period')
periodp<-gvisPieChart(tmp,options = list(width=600,height=400))
return(periodp)
}
```

**D: Calls among date**

```{r results='asis',message=FALSE,warning=FALSE}
DT<-function(item){
  if(item=='All'){
    tmp<-df
  }else{
    tmp<-df[df$Event_type==item,]
  }
tmp<-sqldf('SELECT Date,count(Date) as freq from tmp group by Date')
CalD <- gvisCalendar(tmp,datevar="Date", 
                    numvar="freq",
                    options=list(
                      title="Calls Records Around the Year",
                      width=800,
                      height=440,
                      calendar="{yearLabel: { fontName: 'Times-Roman',
                               fontSize: 32, color: '#1A8763', bold: true},
                               cellSize: 20,
                               cellColor: { stroke: 'red', strokeOpacity: 0.2 },
                               focusedCellColor: {stroke:'red'}}")
                    )
return(CalD)
}
```

**E: Calls among Hours**

```{r,message=FALSE,warning=FALSE}
HR<-function(item){
  if(item=='All'){
    tmp<-df
  }else{
    tmp<-df[df$Event_type==item,]
  }
tmp<-sqldf('SELECT Hour,count(Hour) as freq from tmp group by Hour')
HRP<-gvisColumnChart(tmp,options = list(width=800,height=400))
return(HRP)
}
```

**F:The most frequent calling reasons**

```{r,message=FALSE,warning=FALSE}
RE<-function(item){
tmp<-df[df$Event_type==item,] 
tmp<-sqldf('SELECT Event_detail,count(Event_detail) as freq from tmp group by Event_detail order by freq desc') 
Table <- gvisTable(tmp,options=list(page='enable',width=300,height=600))
return(Table)
}
```

### Now use Google Visulization to see what we want

#### A: Explore All Types of Events

**A: Where do they happen**

```{r,message=FALSE,warning=FALSE}
Map('All')
```

**B:Calls among the week**

```{r results='asis',message=FALSE,warning=FALSE}
days('All')
```

**C:Calls among Day**

```{r results='asis',message=FALSE,warning=FALSE}
period('All')
```

**D: Date Records of the call**

```{r results='asis',message=FALSE ,warning=FALSE}
DT('All')
```

**E:Calls in hours**

```{r results='asis',message=FALSE, warning=FALSE}
HR('All')
```

#### EMS Visulization

**A: Where do they happen**

```{r,message=FALSE,warning=FALSE}
Map('EMS')
```

**B:Calls among the week**

```{r results='asis',message=FALSE,warning=FALSE}
days('EMS')
```

**C:Calls among Day**

```{r results='asis',message=FALSE,warning=FALSE}
period('EMS')
```

**D: Date Records of the call**

```{r results='asis',message=FALSE ,warning=FALSE}
DT('EMS')
```

**E:Calls in hours**

```{r results='asis',message=FALSE, warning=FALSE}
HR('EMS')
```

**F: Details of Calls**

```{r results='asis',message=FALSE, warning=FALSE}
RE('EMS')
```

#### Traffic Visulization

**A: Where do they happen**

```{r,message=FALSE,warning=FALSE}
Map('Traffic')
```

**B:Calls among the week**

```{r results='asis',message=FALSE,warning=FALSE}
days('Traffic')
```

**C:Calls among Day**

```{r results='asis',message=FALSE,warning=FALSE}
period('Traffic')
```

**D: Date Records of the call**

```{r results='asis',message=FALSE ,warning=FALSE}
DT('Traffic')
```

**E:Calls in hours**

```{r results='asis',message=FALSE, warning=FALSE}
HR('Traffic')
```

**F: Details of Calls**

```{r results='asis',message=FALSE, warning=FALSE}
RE('Traffic')
```

#### Fire Visulization

**A: Where do they happen**

```{r,message=FALSE,warning=FALSE}
Map('Fire')
```

**B:Calls among the week**

```{r results='asis',message=FALSE,warning=FALSE}
days('Fire')
```

**C:Calls among Day**

```{r results='asis',message=FALSE,warning=FALSE}
period('Fire')
```

**D: Date Records of the call**

```{r results='asis',message=FALSE ,warning=FALSE}
DT('Fire')
```

**E:Calls in hours**

```{r results='asis',message=FALSE, warning=FALSE}
HR('Fire')
```

**F: Details of Calls**

```{r results='asis',message=FALSE, warning=FALSE}
RE('Fire')
```

